### 2024-02-16 documentation/thesis/thesis_document.tex
.

There are two ways of using the data from the magnets that were
previously measured:

@@

The usecases were defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{usecase-evaluation}, the defined usecases are also used as
a reference to demonstrate the implemented capabilities of the solution.
This is essential for understanding the needs of the target group and
designing the end result accordingly.

@@

The use of analog sensors is purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They were excluded because they require more carefully designed circuits
and more complicated energy management.

@@

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These were performed on a
\emph{RaspberryPi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
Sensor} \ref{d-single-sensor} and the following software settings:

@@

In order to give the user the possibility to display the recorded data
visually, two modules were created, which can graphically prepare
\emph{MRPReading} instances:

@@

During the development of the \gls{mrp}-library, test cases were also
created for all important functionalities and usecases. The test
framework \emph{PyTest} \cite{PyTest} is used for this purpose, as
it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended usecases were mapped using the test cases created, the code
of the test cases could later be used in slightly simplified variants
\ref{lst:pytest_example_code} as examples for the documentation.

@@

One problem, is the parts of the \gls{mrp}-library that require direct
access to external hardware. These are, for example, the \emph{MRPHal}
and \emph{MRPHalRest} modules, which are required to read out sensors
connected via the network. Two different approaches were used here. In
the case of local development, the test runs were carried out on a
\gls{pc} that can reach the network hardware and thus the test run could
be carried out with real data.

@@

In the other scenario, the tests are to be carried out before a new
release in the repository on the basis of \emph{Github Actions}
\cite{GithubActions}. Here there is the possibility to host local
runner software, which then has access to the hardware, but then a
\gls{pc} must be permanently available for this task. Instead, the
hardware sensors were simulated by software and executed via
virtualisation on the systems provided by \emph{Github Actions}.

@@

This process covers all the essential functionalities required for a
comprehensive characterisation of permanent magnets. These were
previously described in the Usecases \ref{usecases} chapter. The
developed framework not only offers a cost-effective and flexible
hardware solution, but also enables customisation of the analysis
algorithms to meet the requirements of different research projects.

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
used for the evaluation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
magnets were used, which are shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png}.

These were placed in modified 3D printed holders
\ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
numbered. This allows them to be matched to the measurement results
later.

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \emph{IP\_return\_count} parameter is set to four, only the four
most similar measurements were exported here. It can be seen from the
plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
\ref{d-fullsphere}.

@@

In addition, the basic application by the user is demonstrated based on
an example. In this way is possible to systematically characterise
magnets from the software and readout hardware side by means of data
acquisition, storage and analysis.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. The additional column for the
\emph{Background-Noise} is taken from the respective data sheets of the
sensors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

@@

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table. For this evaluation, the sensors listed in the table were
used for sensor characterisation. This selection is made for the
following reasons:

@@

It is possible to carry out the sensor characterisation shown here for
other compatible sensors using the same procedure. Pre-configured
measurements \ref{command-line-interface} and analysis pipelines
\ref{programmable-data-processing-pipeline} are available for this
purpose are packaged with library.

@@

The sensor platform used here is an adapted version of the \emph{1D:
Single Sensor} \ref{d-single-sensor} sensor platform. The sensors to be
measured were fixed together on an aluminium plate with thermally
conductive adhesive. This compensates for thermal differences. This is
essential for the subsequent temperature deviation tests in order to
obtain comparable measurement results.

The setup is placed and pre-wired in the temperature chamber 24 hours
before the series of measurements were carried out. The insulated
housing of a \emph{Voron 2.4} 3D printer, which has a separately
controlled internal heating system, is used as the temperature chamber.
To verify the temperature, an additional thermometer \emph{VC-7055BT} is
placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
plate is placed between the floor and the sensor base plate to prevent
direct and uneven heating of the base plate by the heated floor.

The graphic
\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
shows this basic setup, the \emph{Raspberry Pi Pico} shown here is used
as the readout hardware, on which the \emph{Unified Sensor Firmware} is
running. With additional connected switch, its possible to isolate or
select a sensor or both sensors to be queried from the firmware.

A separate battery powered supply is used as low-noise power supply for
the sensors boards. An \emph{Raspberry Pi 4} is used as the host
computer, which is connected to the sensors via a \emph{Hailege
ADUM3160} \gls{usb} isolator and is placed outside the temperature
chamber.

@@

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet environment to minimize external field
interference. The temperature chamber for all noise tests is set to
\(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed \emph{24}
hours before the measurement run in the final measurement configuration
inside of the chamber.

The procedure begins with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{N=10000} measured values is recorded for the baseline
measurement.

The output signal of the sensor is then continuously measured and
recorded. It is important to carry out the measurement over a
sufficiently long period of time in order to record both short-term and
long-term fluctuations. For this purpose, \emph{N=2000} further measured
values were taken with a trigger and readout rate of one measurement per
second.

@@

The following figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
shows the measured values of these sensors. In the following, these are
analysed for each sensor examined.

@@

The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
values that were extracted from the measurement data of the sensors
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
These measured values are categorised below.

@@

It is recommended, however, to use a separate temperature sensor when
using the \emph{TLV493D} or to use a suitable averaging of the
temperature and measured values in order to perform temperature
compensation.

@@

After the sensor baseline has been determined with \emph{N=10000}
samples, the magnet is inserted into the holder. The linear axis is
moved by the user until it is maximally saturated. With the
\emph{TLV493D}, this corresponds to 250.000\(\mu\)T and below in low
resolution mode. \emph{MCC5603NJ} around 3000\(\mu\)T. This ensures that
the linearity is determined over the entire measuring range.

@@

After the measurements were exported, they were analysed for linearity
using \emph{MRPAnalysis} \ref{mrpanalysis} functions.

>>>>

There are two ways of using the data from the magnets that are
previously measured:

@@

The usecases are defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{usecase-evaluation}, the defined usecases are also used as
a reference to demonstrate the implemented capabilities of the solution.
This is essential for understanding the needs of the target group and
designing the end result accordingly.

@@

The use of analog sensors is purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They are excluded because they require more carefully designed circuits
and more complicated energy management.

@@

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These are performed on a
\emph{RaspberryPi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
Sensor} \ref{d-single-sensor} and the following software settings:

@@

In order to give the user the possibility to display the recorded data
visually, two modules are created, which can graphically prepare
\emph{MRPReading} instances:

@@

During the development of the \gls{mrp}-library, test cases are also
created for all important functionalities and usecases. The test
framework \emph{PyTest} \cite{PyTest} is used for this purpose, as
it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended usecases are mapped using the test cases created, the code
of the test cases could later be used in slightly simplified variants
\ref{lst:pytest_example_code} as examples for the documentation.

@@

One problem, is the parts of the \gls{mrp}-library that require direct
access to external hardware. These are, for example, the \emph{MRPHal}
and \emph{MRPHalRest} modules, which are required to read out sensors
connected via the network. Two different approaches are used here. In
the case of local development, the test runs are carried out on a
\gls{pc} that can reach the network hardware and thus the test run could
be carried out with real data.

@@

In the other scenario, the tests are to be carried out before a new
release in the repository on the basis of \emph{Github Actions}
\cite{GithubActions}. Here there is the possibility to host local
runner software, which then has access to the hardware, but then a
\gls{pc} must be permanently available for this task. Instead, the
hardware sensors are simulated by software and executed via
virtualisation on the systems provided by \emph{Github Actions}.

@@

This process covers all the essential functionalities required for a
comprehensive characterisation of permanent magnets. These are
previously described in the Usecases \ref{usecases} chapter. The
developed framework not only offers a cost-effective and flexible
hardware solution, but also enables customisation of the analysis
algorithms to meet the requirements of different research projects.

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
used for the evaluation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
magnets are used, which are shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png}.

These are placed in modified 3D printed holders
\ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
numbered. This allows them to be matched to the measurement results
later.

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \emph{IP\_return\_count} parameter is set to four, only the four
most similar measurements are exported here. It can be seen from the
plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
\ref{d-fullsphere}.

@@

In addition, the basic application by the user is demonstrated based on
an example. Based on this it is possible to systematically characterise
magnets from the software and readout hardware side by means of data
acquisition, storage and analysis.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
are used for sensor characterisation. The additional column for the
\emph{Background-Noise} is taken from the respective data sheets of the
sensors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

@@

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table. For this evaluation, the sensors listed in the table are used
for sensor characterisation. This selection is made for the following
reasons:

@@

It is possible to carry out the sensor characterisation shown here for
other compatible sensors using the same procedure. Pre-configured
measurements \ref{command-line-interface} and analysis pipelines
\ref{programmable-data-processing-pipeline}, which are available for
this purpose, are packaged within the library.

@@

The sensor platform used here is an adapted version of the \emph{1D:
Single Sensor} \ref{d-single-sensor} sensor platform. The sensors to be
measured are fixed together on an aluminium plate with thermally
conductive adhesive. This compensates for thermal differences. This is
essential for the subsequent temperature deviation tests in order to
obtain comparable measurement results.

The setup is placed and pre-wired in the temperature chamber 24 hours
before the series of measurements are carried out. The insulated housing
of a \emph{Voron 2.4} 3D printer, which has a separately controlled
internal heating system, is used as the temperature chamber. To verify
the temperature, an additional thermometer \emph{VC-7055BT} is placed on
the base plate. A \emph{10mm} thick \emph{PTFE} insulation plate is
placed between the floor and the sensor base plate to prevent direct and
uneven heating of the base plate by the heated floor.

The graphic
\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
shows this basic setup, the \emph{Raspberry Pi Pico} is used as the
readout hardware, on which the \emph{Unified Sensor Firmware} is
running. With additional connected switch, its possible to isolate or
select a sensor or both sensors to be queried from the firmware.

A separate battery power supply is used as low-noise power supply for
the sensors boards. An \emph{Raspberry Pi 4} is implemented as the host
computer, which is connected to the sensors via a \emph{Hailege
ADUM3160} \gls{usb} isolator and is placed outside the temperature
chamber.

@@

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet and static environment to minimize external
field interference. The temperature chamber for all noise tests is set
to \(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed \emph{24}
hours before the measurement run in the final measurement configuration
inside of the chamber.

The procedure starts with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{N=10000} measured values is recorded for the baseline
measurement.

The output signal of the sensor is continuously measured and recorded.
It is important to carry out the measurement over a sufficiently long
period of time in order to record both short-term and long-term
fluctuations. For this purpose, \emph{N=2000} further measured values
are taken with a trigger and readout rate of one measurement per second.

@@

The following figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
shows the measured values of these sensors. In the next phases these are
analysed for each sensor examined.

@@

The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
values that are extracted from the measurement data of the sensors
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
These measured values are categorised below.

@@

Though it is recommended to use a separate temperature sensor when using
the \emph{TLV493D} or to use a suitable averaging of the temperature and
measured values in order to perform temperature compensation.

@@

After the sensor baseline has been determined with \emph{N=10000}
samples, the magnet is inserted into the holder. The linear axis is
moved by the user until it is maximally saturated. With the
\emph{TLV493D}, this corresponds to \emph{250.000\(\mu\)T} and below in
low resolution mode. \emph{MCC5603NJ} around \emph{3000\(\mu\)T}. This
ensures that the linearity is determined over the entire measuring
range.

@@

After the measurements are exported, they are analysed for linearity
using \emph{MRPAnalysis} \ref{mrpanalysis} functions.
